{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-13 paper/paper.tex
added citation in the explanation of the structure
paragraph about security levels

\section{Introduction to research area}
\label{sec:introduction}
\section{Summary of the article}
\label{sec:discussion}
In this summary I will follow mainly the structure of the original
paper which is as follows. After the introduction the basic terms and
definitions for a multithreaded programs and the scheduler are laid.
After that the notion of security we want to achieve is presented. Along
with this a skeleton of a type system is described, which ensures that a
program typable in this type system is secure w.r.t the notion of security.
The proof that this holds is sketched in the following section. In the
last section the (by now) abstract framework is instantiated with a
concrete example.

@@

>>>>

\section{Introduction to research area}
\label{sec:introduction}
\section{Summary of the article}
\label{sec:discussion}
In this summary I will follow mainly the structure of the original
paper\cite{Barthe07} which is as follows. After the introduction the basic
terms and definitions for a multithreaded programs and the scheduler are
laid. After that the notion of security we want to achieve is presented.
Along with this a skeleton of a type system is described, which ensures
that a program typable in this type system is secure w.r.t the notion of
security. The proof that this holds is sketched in the following section.
In the last section the (by now) abstract framework is instantiated with a
concrete example.

@@

The next thing introduced are the security levels. We assume the attacker
'is' a level $k$. From this assumption we can reduce every set of levels
w.l.o.g into $\{low, high\}$, where $low < high$, by mapping elements
that are no more sensitive than $k$ to $low$ and all other elements
including incomparable ones to $high$.
